---
title: "Data Visualizations by Andrea Evans and Tallis Moore"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(scales)
```

Benford's Law
=======================================================================

Column
----------------

### Benford's Law Distribution of Leading Digit

```{r}
readRDS("BenfordsLaw.rds")
```


Inputs {.sidebar}
-----------------------------------------------------------------------
### What is Benford's Law?

Benford’s Law, or the first-digit law, 
recognizes a pattern in numerical data. 
Essentially, it observes that 
the leading digit of a number 
is disproportionately likely to be small, 
with 1 appearing as the first digit roughly 30% of the time.
This law applies over a wide variety of data sets,
including building heights, street addresses,
prices, and population numbers. 
It has been used to identify fraud in cases such as accounting, as artificial data 
may not conform to Benford’s Law.


Seattle City Council Ages
=======================================================================

Column
------------------

### Ages of Seattle Council Members (2023)

```{r}
readRDS("CityCouncilAge.rds")
```

Best States to Work in the USA
=======================================================================
Column
------------------

### Oxfam's Ranking of Labor Laws in Each State

```{r}
readRDS("USWorkMap.rds")
```


